Results

### 2024-04-26 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
```

@@

```{r}
## The plot
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4)
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = rev(fancy_names))
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE, message = FALSE}
require(psych)

>>>>

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
#rm1 = "extant", rm2 = "historic", rm3 = "prehistoric"

#TODO: reorder so to have rm2, rm3, rm1

@@

```{r}
## The plot
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = rev(fancy_names), , pch = c(19,15,17))
dev.off()
```

Figure 3: Empirical data. Plain circles represents the metric for historic data (53 % - 63/118 species), lightly fainted squares for prehistoric data (46% - 55/118 species), and fainted triangles for extant data (31% - 37/118 species).
<!-- TODO: this caption is for the empirical data re-arranged as rm2, rm3, rm1 -->

@@

```{r, eval = FALSE, echo = FALSE, message = FALSE}
require(psych)
